Capstone Movielens Report

### 2025-05-16 reports/capstone-movielens.site/04.appendix.Rmd
Minor fix.

```{r eval=FALSE}
data.plot(data, 
          title, 
          xname, 
          yname, 
          xlabel = NULL, 
          ylabel = NULL,
          line_col = "blue",
          # scale = 1,
          normalize = FALSE)
```
:::

::: { #func.data.plot.params .sidebar }
#### Parameters
\
::: { #func.mean_reg.params.param1 .sidebar }
  - **param1:** description;

@@

The soure code of the [data.plot]() function is shown below:
```{r eval=FALSE}
data.plot <- function(data, 
                      title, 
                      xname, 
                      yname, 
                      xlabel = NULL, 
                      ylabel = NULL,
                      line_col = "blue",
                      # scale = 1,
                      normalize = FALSE) {
  y <- data[, yname]

@@

::: { #func.fname00.params .sidebar }
#### Parameters
\
::: { #func.fname00.params.param1 .sidebar }
  - **param1:** description;

>>>>

```{r eval=FALSE}
data.plot(data, 
          title, 
          xname, 
          yname, 
          xlabel = NULL, 
          ylabel = NULL,
          line_col = "blue",
          normalize = FALSE)
```
:::

::: { #func.data.plot.params .sidebar }
#### Parameters
\

::: { #func.mean_reg.params.param1 .sidebar }
  - **param1:** description;

@@

The soure code of the [data.plot]() function is shown below:
```{r eval=FALSE}
data.plot <- function(data, 
                      title, 
                      xname, 
                      yname, 
                      xlabel = NULL, 
                      ylabel = NULL,
                      line_col = "blue",
                      normalize = FALSE) {
  y <- data[, yname]

@@

::: { #func.fname00.params .sidebar }
#### Parameters
\

::: { #func.fname00.params.param1 .sidebar }
  - **param1:** description;
